---
title: "Ad hoc bits for revision"
output:
  html_document:
    df_print: paged
---


```{r "set up", include = FALSE}
# Chunk options
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# Packages
library(tidyverse)
```

**Load the data**

Load the `analyticData.csv` which was the basis for the analysis. 

```{r "load analyticData"}
analyticData <- readr::read_csv("../1.DataPreparation/analyticData.csv")
```

<br>

**Reviewer 1**

*9.  Where are the non-invasive hemodynamic comparisons in table 1?  Without listing these for each group and meaningful comparisons of toe pressures etc then this is incomplete

Response: WIfI ischemia grades are already provided in table 1. Additionally, we have now provided the mean and median toe pressures for each group. 

To get the toe pressures, we need to map back the analytic data to the original data MRNs and then look at the master patient file with the toe pressures.

```{r "mean and median toe pressures"}
# ptNum to MRN crosswalk
mrnCrosswalk <- readxl::read_xlsx("/Volumes/McGinigle_Kate_IRB18-1153/Analysis/Data_for_Siyeon/MRN_to_PtNum_crosswalk.xlsx")
# Toe pressures are in the master patient file from the staging project
masterPtData <- readxl::read_xlsx("/Volumes/McGinigle_Kate_IRB18-1153/_IRB18-1153_PROJECT_DATA/IRB18-1153_MASTER_PATIENT_WITH_ATA_PTA_TOE_PRESSURE.xlsx",skip = 3)

# Collect what we need for the toe pressures
toePressures <- analyticData %>%
  select(ptNum, primaryProcedure, hemodynamicLaterality) %>%
  # Crosswalk ptNum to MRN
  left_join(mrnCrosswalk, by = "ptNum") %>%
  # Merge analytic data with master patient file on MRN, keep only toe pressures
  left_join(masterPtData %>%
              select(CURRENT_MRN, 
                     RT_GREAT_TOE_PRESSURE, 
                     LT_GREAT_TOE_PRESSURE), by = "CURRENT_MRN") %>%
  mutate(toePressure = if_else(hemodynamicLaterality == "Right", RT_GREAT_TOE_PRESSURE, LT_GREAT_TOE_PRESSURE))

# Toe pressures by group
toePressures %>%
  mutate(toePressure = as.numeric(toePressure)) %>%
  group_by(primaryProcedure) %>%
  summarise(meanTP = mean(toePressure, na.rm = TRUE),
            medianTP = median(toePressure, na.rm = TRUE),
            sdTP = sd(toePressure, na.rm = TRUE),
            minTP = min(toePressure, na.rm = TRUE),
            maxTP = max(toePressure, na.rm = TRUE),
            missingTP = sum(is.na(toePressure)),
            n = n())

# Toe pressures for overall cohort
toePressures %>%
  mutate(toePressure = as.numeric(toePressure)) %>%
  summarise(meanTP = mean(toePressure, na.rm = TRUE),
            medianTP = median(toePressure, na.rm = TRUE),
            sdTP = sd(toePressure, na.rm = TRUE),
            minTP = min(toePressure, na.rm = TRUE),
            maxTP = max(toePressure, na.rm = TRUE),
            missingTP = sum(is.na(toePressure)),
            n = n())
```
<br>

**Reviewer 3**

Standard considerations such as anatomic location and extent of atherosclerosis, body habitus, and availability of adequate autogenous vein conduit contributed to the shared decision making for type of revascularization. Endovascular revascularizations included approaches from contralateral femoral artery, ipsilateral femoral artery, and/or ipsilateral pedal arteries and interventions included angioplasty, stenting, and atherectomy as indicated. Open surgical cases preferentially used single segment saphenous vein conduit, but also included spliced vein conduits, and in rare circumstances non-autogenous conduits.

Response: Additionally, in the results we added the breakdown of number of revascularizations that were open versus endo. 

To get the number of endos vs opens, we crosswalk the analytic data ptNums to the MRNs. Then we use the procedure csv to find out the procedure.

```{r "Number endo vs open"}
procedures <- readxl::read_xlsx("/Volumes/McGinigle_Kate_IRB18-1153/Analysis/5.Outcome_creation/procedure.xlsx")

ptsAndProcedures <- analyticData %>%
  select(ptNum, primaryProcedure, hemodynamicLaterality) %>%
   # Crosswalk ptNum to MRN
  left_join(mrnCrosswalk, by = "ptNum") %>%
  # Create ptSide
  mutate(ptSide = paste0(CURRENT_MRN, hemodynamicLaterality)) %>%
  left_join(procedures, by = "ptSide") %>%
  mutate(procedure = if_else(Endovascular == 1 & Open == 1, "both", "?"),
         procedure = if_else(Endovascular == 1 & Open == 0, "Endo", procedure),
         procedure = if_else(Endovascular == 0 & Open == 1, "Open", procedure),
         procedure = if_else(procedure == "?", "WM", procedure)) 

ptsAndProcedures %>% count(procedure)

# For patients that had both endo and open, find out which came first
hadEndoAndOpenMRNs <- ptsAndProcedures %>% 
  filter(procedure == "both") %>%
  select(CURRENT_MRN)

allProcedures <- readxl::read_xlsx("/Volumes/McGinigle_Kate_IRB18-1153/_IRB18-1153_PROJECT_DATA/IRB18-1153_PROCEDURES.xlsx", skip = 3)
source("/Volumes/McGinigle_Kate_IRB18-1153/Analysis/scripts/groupProcedures.R")

multProcPts <- allProcedures %>% 
  # Filter to only the patients we are interested in
  filter(CURRENT_MRN %in% hadEndoAndOpenMRNs$CURRENT_MRN) %>%
  # Only keep procedures on or after dx
  mutate(DAYS_FROM_CLI_DX = as.numeric(DAYS_FROM_CLI_DX)) %>%
  filter(DAYS_FROM_CLI_DX >= 0) %>%
  # group the procedures
  groupProcedures() %>%
  # Keep only the ends and opens
  filter(procGroup %in% c("Endovascular", "Open")) %>%
  # pick the earliest of endo or open
  mutate(PROCEDURE_DATE = lubridate::as_date(PROCEDURE_DATE)) %>%
  group_by(CURRENT_MRN) %>%
  filter(PROCEDURE_DATE == min(PROCEDURE_DATE))  %>%
  select(CURRENT_MRN, procGroup) %>%
  distinct() %>%
  group_by(CURRENT_MRN) %>%
  add_count()

# Per e-mail from Kate, all of these can be considered as open
allProcedures %>%
  filter(CURRENT_MRN %in% multProcPts$CURRENT_MRN[multProcPts$n > 1]) %>%
  # Only keep procedures on or after dx
  mutate(DAYS_FROM_CLI_DX = as.numeric(DAYS_FROM_CLI_DX)) %>%
  filter(DAYS_FROM_CLI_DX >= 0) %>%
  # group the procedures
  groupProcedures() %>%
  group_by(CURRENT_MRN) %>%
  filter(PROCEDURE_DATE == min(PROCEDURE_DATE)) 

  
```


-	Also, cross over rates and at what time?

Response: The number of patients who were initially treated with wound care alone, who went on to require revascularization for non-healing wounds was XX. The median time to delayed revascularization was XX.

```{r "crossovers from wm to revasc"}

wmPts <- analyticData %>% filter(primaryProcedure == "WM") %>%
  left_join(mrnCrosswalk, by = "ptNum")

# Patients that initially had wm and eventually had a revasc
wmToRevasc <- wmPts %>% select(ptNum, ptSide, hemodynamicLaterality, CURRENT_MRN) %>%
  left_join(allProcedures, by = "CURRENT_MRN") %>%
  mutate(DAYS_FROM_CLI_DX = as.numeric(DAYS_FROM_CLI_DX)) %>%
  filter(DAYS_FROM_CLI_DX >= 0) %>%
  groupProcedures() %>%
  group_by(CURRENT_MRN) %>%
  count(procGroup) %>%
  pivot_wider(names_from = procGroup, values_from = n) %>%
  select(-c(other, Fasciotomy)) %>%
  replace_na(list(Debridement = 0,
                  `Minor amputation` = 0,
                  Endovascular = 0, 
                  `Major amputation` = 0,
                  `Open` = 0)) %>%
  mutate(hadRevasc = if_else(Endovascular + Open > 0, 1, 0)) %>%
  ungroup() %>%
  filter(hadRevasc == 1)
  
allProcedures %>%
  filter(CURRENT_MRN %in% wmToRevasc$CURRENT_MRN) %>%
  mutate(DAYS_FROM_CLI_DX = as.numeric(DAYS_FROM_CLI_DX)) %>%
  filter(DAYS_FROM_CLI_DX >= 0) %>%
  groupProcedures() %>%
  filter(procGroup %in% c("Endovascular", "Open")) %>%
  mutate(PROCEDURE_DATE = lubridate::as_date(PROCEDURE_DATE)) %>%
  group_by(CURRENT_MRN) %>%
  filter(PROCEDURE_DATE == min(PROCEDURE_DATE)) %>%
  select(CURRENT_MRN, PROCEDURE_DATE, DAYS_FROM_CLI_DX, procGroup) %>%
  distinct() %>%
  ungroup() %>%
  summarise(median(DAYS_FROM_CLI_DX))
```




